Methods

### 2021-09-17 Manuscript/Manuscript_Methods.Rmd
better explanation of simple ordering

### Record's acquisition and initial labelling
We built a set of tools to let users automatically search and download records data from three major scientific databases ("sources"): MEDLINE (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>). The user needs to input a search query and a date range. The query may contain boolean operators AND, OR, NOT and nested parentheses.\
For WOS, an Application Programming Interface (API) key is necessary to use the automatic search tools; for IEEE, if an API key is not available, a slower, web scraping-based solution will be employed; for MEDLINE, an API key is required only for high-frequency requests to the NCBI server [@pubmed], or if a large number of records is expected since our tool splits big API requests in multiple smaller ones.\
It is also possible to download and import records in the framework manually. This is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/search/form.uri?display=basic#basic>) and EMBASE databases (<https://www.embase.com/#advancedSearch/default>), for which a comprehensive API interface was not easy to build. A short guide on how to set up the framework for each supported database is available in Supplemental Material S3.\
Once the records are downloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources, ordering the records by simple query term frequency ("simple ordering"), putting the most likely relevant records on top. The output is an "Annotation file".\

@@

The automatic classification task and the manual review step form an iterative loop (CR iterations). The whole algorithm falls in the pattern defined as active machine learning [@settles2009active, miwa2014reducing], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
The CR iterations continue until no new positive matches are found in four consecutive iterations. The framework supports alternative stopping conditions like limits on the fraction or number of total records reviewed and on the total number of positive matches found.

>>>>

### Record's acquisition and initial labelling
We built a set of tools to let users automatically search and download records data from three major scientific databases ("sources"): MEDLINE (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>). The user needs to input a search query and a date range. The query may contain boolean operators AND, OR, NOT and nested parentheses.\
For WOS, an Application Programming Interface (API) key is necessary to use the automatic search tools; for IEEE, if an API key is not available, a slower, web scraping-based solution will be employed; for MEDLINE, an API key is required only for high-frequency requests to the NCBI server [@pubmed], or if a large number of records is expected since our tool splits big API requests in multiple smaller ones.\
It is also possible to download and import records in the framework manually. This is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/search/form.uri?display=basic#basic>) and EMBASE databases (<https://www.embase.com/#advancedSearch/default>), for which a comprehensive API interface was not easy to build. A short guide on how to set up the framework for each supported database is available in Supplemental Material S3.\
Once the records are downloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources. The records are ordered according to the frequency of the positive terms (e.g., not preceded by a $NOT$ modifier) of the query appear in the title and abstract ("simple ordering"); this approach is a modification of @wallace2010active. The final output is an "Annotation file" with all the record's info and its label when present´.\

@@

The automatic classification task and the manual review step form an iterative loop (CR iterations). The whole algorithm falls in the pattern defined as active machine learning [@settles2009active, @miwa2014reducing], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
The CR iterations continue until no new positive matches are found in four consecutive iterations. The framework supports alternative stopping conditions like limits on the fraction or number of total records reviewed and on the total number of positive matches found.
